%%%
\subsection{Feature Binning}

Above we illustrated how the \verb|HOSPITAL| field had nine attributes, but we put them into two bins.  We were interested only in whether a crash person was transported to a hospital, not exactly how, so for our purposes, ``EMS Air'' and "EMS Ground'' were equivalent.  Several of the features had about ten attributes that we could assign to fewer bins in obvious ways.  Details in the technical paper.

Some features had attributes that did not fall into bins in obvious ways.  Is a ``Compact Pickup,'' a designation that only existed in 2016, more like a sedan or a light pickup?  To draw the lines, we looked at how that attribute correlated with \verb|HOSPITAL|.  The rate at which crash persons in compact pickups were transported to the hospital was (statistically) indistinguishable from sedans (15\%), but very different from light pickups (11\%).  

For \verb|AGE_IM|, age with missing values imputed, we had values 0-120 that we wanted to assign to bins.  The obvious way would have been to do it by decade, but when we looked at the hospitalization rates, patterns emerged.  

In most states in the US, teens can get a driver's license at age 16, but in most states they can get a learner's permit earlier, so in the chart below, some of the 14 and 15 year olds may be the driver.  

In the chart, we see a big shift between 14 and 16, both in the number of crash people and the hospitalization rate.  There is also a big shift between 18 and 21 in hospitalization rate.  Where exactly to draw the line is open for debate, but we made 16-18 a separate group.  The next big shift was in the 50's, and we made 19-52 the next group.  

\begin{center}
\begin{tabular}{lll}
	\multicolumn{2}{l}{Age} \cr
	& \multicolumn{2}{l}{Percent of Total Crash Persons} \cr
	&& Hospitalization Rate (\%) \cr\hline
	 10 & 0.53 & 16.58 \vrule width 0pt height 10pt\cr
	 11 & 0.51 & 15.51 \cr
	 12 & 0.52 & 16.54 \cr
	 13 & 0.54 & 16.72 \cr
	 14 & 0.63 & 17.56 \cr
	 15 & 0.88 & 15.21 \cr
	 16 & 1.65 & 13.46 \cr
	 17 & 2.18 & 14.25 \cr
	 18 & 2.65 & 14.41 \cr
	 19 & 2.67 & 15.47 \cr
	 20 & 2.58 & 14.91 \cr
	 21 & 2.51 & 15.65 \cr
	 22 & 2.56 & 15.43 \cr
	 23 & 2.44 & 15.57 \cr
	 24 & 2.38 & 16.01 \cr
	 25 & 2.37 & 15.50 \cr
\end{tabular}
\end{center}

Full chart in the technical paper.  


