%%%%%
\section{CRSS Binning and Imputing:  Order of Operations}

The HOSPITAL feature has nine values, one representing that we know the person was not transported to a hospital, six representing that we  know the person was transported, and two representing that we don't know.  

We will want to impute those unknowns and bin the feature into a binary with 0 for Not Transported and 1 for Transported.  

\vskip 12pt

\hfil\begin{tabular}{clrl}
	\multicolumn{4}{l}{\bf HOSPITAL Feature} \cr\hline
	Original & Bin & Number of & Meaning \cr
	Value & & Samples & \cr\hline
	0 & 0 & 522,801 & Not Transported \cr
	1 & 1 & 2,549 & EMS Air \cr
	2 & 1 & 605 & Law Enforcement \cr
	3 & 1 & 30,368 & EMS Unknown Mode \cr
	4 & 1 & 8,926 & Transported Unknown Source \cr
	5 & 1 & 61,162 & EMS Ground \cr
	6 & 1 & 4,341 & Other \cr
	8 &  & 12,447 & Not Reported \cr
	9 &  & 1,075 & Reported as Unknown \cr	
\end{tabular}

\vskip 12pt

Before we do the binning and imputing, we need to decide which to do first.  Do we impute unknown values 8 and 9 into \{0, 1, 2, 3, 4, 5, 6\}, then condense \{1,2,3,4,5,6\} into \{1\}, or do we condense \{1,2,3,4,5,6\} into \{1\}, then impute 8 and 9 into \{0,1\}?  Would they give the same results?  Would we be able to determine how much of the difference is due to randomness in the imputation algorithm?  

For some features we had to do the binning first, because the feature had too many categories for IVEware to handle.  The feature MAKE has 70 values, and MOD\_YEAR has 83.  Some experimentation and conversations with IVEware staff showed that fewer that forty categories was possible.  The CRSS Imputation report describes how the CRSS authors did that with AGE, putting it into bins by decade, imputing missing values, then putting back the known values.  \cite{CRSS_Imputation}


I asked Dr. Raghavan which should come first, binning or imputing, and he told me that the answer depends on the data, and I should experiment.  He sent me a paper on the topic by one of this students.  I plan to experiment and decide which to use.  My gut hypothesis is that binning first would be better, but we will not see a definitive difference in the test results.  

To Do:  \index{To Do!Order of Operations}  Investigate Order of Operations for binning and imputation.



