%%%
\section{CRSS in the Literature}
\label{sec:CRSS_Literature}

\begin{itemize}
	\item Torpuz and Delen (2021) \cite{TOPUZ2021113557} does a thorough description of imputing missing data in CRSS.  Does not mention IVEware.  Also deals with imbalanced data well.  Need to spend time with this article. 

	\item Cox and Cicchino (2021) \cite{COX2021288} says CRSS ``can be
weighted to produce annual national estimates.''  Also, ``Police-reported
crash sampling methods changed when NHTSA converted from
NASS GES to CRSS, which may have affected the comparability of
the 2017 data on all crash involvements with earlier years.''
	
	In this study, 
	``Imputed data were utilized when available to account for missing data.''
	
	\item Amini, Bagheri, and Delen (2022) \cite{AMINI2022108720} gives a thorough description of CRSS.  They took out CRSS-imputed variables.  Also removed post-accident information, as it was not relevant.  They imputed missing continuous variables, but don't say how.  They left missing categorical variables as ``Unknown'' and ``Missing'' categories.  
	
\begin{quote}
	Employing descriptive analytics, we distinguished and removed
variables with a large percentage of missing values (more than 70\%), as
well as the identification, irrelevant, repetitive, and CRSS-imputed
variables. We also removed the variables with post-accident information,
such as whether the vehicle was towed afterward or the number of
injured people. Using such variables contradicts the basic assumption of
time order in causal relations, where a cause should precede its effect.
Furthermore, we handled other missing values by considering them
separate categories for nominal variables and imputing numeric ones.
\end{quote}	

	\item Spicer et al (2021) \cite{SPICER2021105974} used CRSS but did not mention missing or imputed data.  
	
	\item Villavicencio, Svancara, Kelly-Baker, and Tefft (2022) \cite{VILLAVICENCIO2022757} says that ``CRSS is a representative
sample of all police-reported crashes in the United States,'' which is not true.  They used FARS and CRSS as their primary data sources, but did not mention imputed or missing data.  
	
	\item Mueller and Cicchino (2022) \cite{MUELLER2022305} says that  ``The CRSS data set handles missing data for some variables by statistically imputing values, which were used when available.''
	
	\item Kaplan et al \cite{KAPLAN2017130} uses the phrase, ``restricted access database.''  I should use that for the Louisiana crash database.  
	
	\item  Gong et al \cite{GONG2022100190} just dropped samples with missing values.  
	
	\item As far back as 2002, NHTSA was working on multiple imputation methods for its related database, FARS.  \cite{subramanian2002transitioning}
		
\end{itemize}
