%%%%% One-Page Summary
\section*{One-Page Summary}

Problem:  Given an automated crash report from a cell phone, use two historical datasets to build and analyze models to recommend whether to immediately dispatch an ambulance.  The solution requires data cleaning, imputing unknown values, and handling imbalanced data.

\begin{enumerate}
	\item I am qualified and on track to graduate in December 2023.  See \hyperref[sec:Qualifications]{Qualifications}.
	
	\item My dissertation will demonstrate competence in the major techniques of research.
	\begin{enumerate}[label=\alph*., partopsep=0pt,topsep=0pt,parsep=0pt]
		\item Finding an interesting question whose answer requires current and novel methods
		\item Literature review
		\item Finding appropriate datasets
		\item Data cleaning and imputation of missing values
		\item Handling imbalanced data
		\item Building, testing, and comparing models
		\item Analysis of results in terms of the application
		\item Analysis of results in terms of the current and novel methods
	\end{enumerate}
	
	\item My dissertation will make novel contributions to the field.
	\begin{enumerate}[label=\alph*., partopsep=0pt,topsep=0pt,parsep=0pt]
		\item Novel application
		\item Previously unused method for 
		\hyperref[sec:CRSS_Imputing]{imputing unknown values} in a major dataset
		\item New metrics:  
		\hyperref[sec:Balanced_Metrics]{Balanced precision and balanced F1}
		\item New interpretation of class weights as a 
		\hyperref[sec:Ethical_Tradeoff]{political and ethical cost-benefit tradeoff}	
	\end{enumerate}
	
	\item My dissertation will demonstrate that I have wrestled with the data in these aspects that are as much art as science.
	\begin{enumerate}[label=\alph*., partopsep=0pt,topsep=0pt,parsep=0pt]
		\item \hyperref[sec:CRSS_Imputing]{Imputing} missing values
		\item \hyperref[sec:CRSS_Binning]{Binning} (discretizing, batching) many categories into fewer
		\item \hyperref[sec:CRSS_Order_of_Operations]{Order of operations} for imputing and binning
		\item Handling \hyperref[sec:Focal_Loss_and_Tomek]{imbalanced data}
	\end{enumerate}
	
	\item I have reviewed the literature in these areas.
	\begin{enumerate}[label=\alph*., partopsep=0pt,topsep=0pt,parsep=0pt]
		\item \hyperref[sec:Imbalanced_Metrics]{ML metrics for imbalanced data}
		\item \hyperref[sec:Lit_Review_Imbalanced]{Dataset balancing techniques}
		\item \hyperref[sec:CRSS_Literature]{Others' use of the CRSS dataset} and how they handled missing data
		\item Use of the metrics and imbalanced data techniques in the \hyperref[sec:Crash_Imbalanced_Papers]{crash analysis literature}
	\end{enumerate}
	
	\item I am preparing a paper for submission to a 
	\hyperref[sec:Journals]{respected journal}.  See accompanying draft.  I want the paper to be a model of open science, with a technical paper and clean code available on GitHub.
	
	\item I have a detailed and realistic \hyperref[sec:Research_Plan]{plan}
	for completing the dissertation.  
	
	\item This document and the accompanying paper draft illustrate that I can make useful large documents to different specifications.  

	\item I have more questions than answers.  
\end{enumerate}