%%%%%
\section{Algorithm Level Approaches}

%%%
\subsection{Some Papers}
\begin{itemize}
	\item Recognition-based:  Learning from one class rather than discrimination-based, doing unsupervised learning on the minority class. \cite{CHAWLA_2004}
	\item Fuzzy rule-based classification systems (what is this?)
		\cite{CHABBOUH_2019} 
		\cite{DABLAIN_2021}
		\cite{MAHMUDAH_2021} 
		\cite{ZHAI_2020} 
		\cite{ZHAI_2020_D2GAN}
	\item In decision trees, using evolutionary/genetic methods instead of greedy search 
		\cite{CHABBOUH_2019} 
		\cite{WEISS_2000}
	\item Clustering and Subspace Modeling \cite{CHEN_2011}
\end{itemize}

%%%
\subsection{Genetic Algorithms}

In this short 2000 paper, Weiss \cite{WEISS_2000} used a genetic algorithm to predict rare events. Borrowing from simulated annealing, they varied the relative importance of precision and recall at each step of the genetic algorithm.  

%%%
\subsection{Subspace Model}

Chen 2011 \cite{CHEN_2011}

This was fascinating and entirely different from anything I've seen.  

\begin{enumerate}
	\item Separate the training data $Tr$ into negative (majority) and positive (minority) classes $TrN$ and $TrP$.
	\item Let $K$ be the ratio of negative to positive samples, in my case about 100, so that if you divide the majority class $TrN$ into $K$ groups, each will have about the same number of samples as the minority class.
	\item Use $K$-means clustering to separate the negative (majority) class $TrN$ into $K$ groups; each of the groups is a cluster of the negative (majority) class.
	\item For each of the $K$ groups $TrN_i$:
	\begin{itemize}
		\item Combine the negative elements of the group with the entire positive (minority) class $TrP$ to form a balanced subspace.  
		\item Train the model for the subspace
	\end{itemize}
	\item Recombine the $K$ subspace models with a model trained on the entire data set to build an integrated model.
\end{enumerate}
