%%%%%
\section{Crash Datasets}

\begin{itemize}
	\item SHRP2,  Strategic Highway Research Program 2, Naturalistic Driving Study
	
	Federal Department of Transportation
	
	Most cited dataset.  
	
	\item Second Highway Research Program (Data Set)
	
	I have an account.  
	\item Virginia 100-car Database 
	\item Next Generation Simulation, NGSIM Trajectory Data
	https://iswitrs.chp.ca.gov/Reports/jsp/index.jsp
	\item NASS-CDS:  National Automotive Sampling System – Crashworthiness Data System
	\item Canada's National Collision Database
	\item Michigan Safety Pilot
	\item Roadway Information Database (RID)
	\item Shanghai Naturalistic Driving Study	
	\item California Statewide Integrated Traffic Records System (SWITRS)
	
	Apparently anyone can get an account?
	
	\url{https://iswitrs.chp.ca.gov/Reports/jsp/index.jsp}
	\item Highway Safety Information System
	
	Not updated since 2018?
	
	\url{http://www.hsisinfo.org}
\end{itemize}

From \verb|24_May_2021_Report|:

%%%%%
\subsection{Jargon to Understand}

\begin{itemize}
	\item Naturalistic Driving Data - Data collected from sensors installed in the driver's own car, trying to get as close as possible to the driver's ``natural'' behavior. \index{Naturalistic Driving Data}
	\item Heterogeneity.  I understand vaguely what ``data heterogeneity'' means, but I'm going to watch for the term to see how it's used in the context of these papers.  \index{Heterogeneity}
\end{itemize}

%%%%%
\subsection{IRB, SHRP Database}

Eleven of the papers in {\it Accident Analysis and Prevention} used the Strategic Highway Research Program 2 (SHRP2) Naturalistic Driving Study (NDS), which put sensors in 3400 cars and recorded five million trips, including crashes.  To get ``Qualified Researcher Status'' with ``full access to data that has been made available through the SHRP 2 NDS Data Access Website,'' I had to submit a certificate of training on research with human subjects.  I did the training through the UL Institutional Review Board (IRB). I now have access.  

%%%%%
\subsection{NGSIM Database}

Three papers use the Next Generation Simulation dataset from the US Dept of Transportation, and it's available for download with no restrictions.  


