%%%%%
\section{Examples of Good Writing, Models to Follow}

\begin{itemize}
	\item Elassad 2020 \cite{ELAMRANIABOUELASSAD2020102708} is a good model.	

	\item Paez 2021 \cite{PAEZ2020105666} is not ML, but a solid paper.  The conclusion suggests looking into imbalanced learning.  
	
	\item Soleimani (LSU) 2019 \cite{SOLEIMANI201965} gives a thorough analysis.
\end{itemize}

\subsection{Elassad 2020}

Good model to follow.

\begin{itemize}
	\item In the title and first sentence of the abstract talks about an application, Collision Avoidance Systems, that the paper does not work with directly, which is like what I'm doing with mobile phones.  
	\item Has several glaring mistakes, like crash avoidance systems on the vehicle having access to data from loop detectors, which are embedded under the road.  
	\item Projects into the future, assuming that vehicles will detect the physiological state of the driver.  I do this when I assume that police departments will have access to up-to-date and well-calibrated maps, to personal data from phone companies, and to be able to corollate several pieces of data (from multiple phones) in real time.  
	\item Critique:  Doesn't define terms well.  What is an ``ensemble fusion framework''?  How are ``ensemble'' and ``fusion'' different?  In layman's language, they sound the same.  Uses ``fusion'' to mean both classifier ensembles and data fusion.
	\item Good overview at the end of the Introduction.  
	\item The ML guts of this paper are trying different combinations of classifiers for an ensemble method.  The guts of my paper will be different combinations of imbalanced data techniques.
	\item Only uses two imbalanced data techniques:  Class weights and SMOTE.
	\item Algorithms
	\item Table of features
	\item Six points for future research
\end{itemize}

